\textsf{Are large language models superhuman chemists?}

### 2024-10-31 src/tex/appendix.tex
fix: skillset composition fig
fix: skillset composition fig (#95)

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V1.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

@@

    \caption{\textbf{Examples for each required skill considered in the \chembench corpus.} The table shows the number of questions for each skill and an example question. Note that the total count in this table is bigger than the \chembench corpus. This is because the same question can be annotated with two different skills, e.g., Reasoning and Calculation.}    \label{tab:chembench_corpus_cognitive} \\

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_FINAL_SKILL_flat.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

@@

    \caption{\textbf{Examples for each required skill considered in the \chembench corpus.} The table shows the number of questions for each skill and an example question. Note that the total count in this table is bigger than the \chembench corpus. This is because the same question can be annotated with two different skills, e.g., Reasoning and Calculation.}    
    \label{tab:chembench_corpus_cognitive} \\
